### 2013-05-21 drafts/general_writeup/writeup.tex
Minor changes to writeup.
Started section on Genetic Programming in the general writeup.

Moreover, we should be able to use previously learned programs to help
us search for new programs. This phenomenon, in which a previously
learned datum is used to represent a later learned datum, we will term
\emph{bootstrapping}. We say that $x$ \empth{bootstraps} $y$ if the
conditional Kolmogorov complexity $K(y|p_x) < r$ when $U(p_x) = x$ and
$r$ is again our resource bound.

@@

\section{Model of Computation: Combinatory Logic}
The representational language and related computational model used to
implement our learner is a typed Combinatory Logic
(CL)~\cite{hindley1972introduction}. CL is symbolic model of
computation that is similar to the more popular $\lambda$-calculus,
but, for our purposes, has one very significant difference: it does
not contain variables. $\lambda$-calculus has three basic syntactic
features -- variables, applications, and abstractions -- that
correspond appealingly with intuitions from mathematics and functional
programming. But besides the semantic difficulties that variables
cause (documented elsewhere), variables additionally complicate the
modularity and compositionality of expressions written in
$\lambda$-calculus. Program induction requires the efficient search
over expressions in the chosen model of computation; being able to
treat most subexpressions of well-formed expressions as themselves
well-formed expressions makes things easier. This was first noticed by
Briggs and O'Neill in using combinators for genetic
programming~\cite{briggs2006functioinal}.

@@

>>>>

Moreover, we should be able to use previously learned programs to help
us search for new programs. This phenomenon, in which a previously
learned datum is used to represent a later learned datum, we will term
\emph{bootstrapping}. We say that $x$ \emph{bootstraps} $y$ if the
conditional Kolmogorov complexity $K(y | p_x) < r$ when $U(p_x) = x$ and
$r$ is again our resource bound.

@@

\section{Model of Computation: Combinatory Logic}
The representational language and related computational model used to
implement our learner is a typed Combinatory Logic
(CL)~\cite{hindley1972introduction}. CL is symbolic model of
computation that is similar to the more popular $\lambda$-calculus,
but, for our purposes, has one very significant difference: it does
not contain variables. $\lambda$-calculus has three basic syntactic
features -- variables, applications, and abstractions -- that
correspond appealingly with intuitions from mathematics and functional
programming. But besides the semantic difficulties that variables
cause (documented elsewhere), variables additionally complicate the
modularity and compositionality of expressions written in
$\lambda$-calculus. Program induction requires the efficient search
over expressions in the chosen model of computation; being able to
treat most subexpressions of well-formed expressions as themselves
well-formed expressions makes things easier. This was first noticed by
Briggs and O'Neill in using combinators for genetic
programming~\cite{briggs2006functional}.

@@

\section{Genetic Programming}

The most directly related work to ours is that on Genetic Programming.
Therefore, we need to declare the differences between our work and genetic
programming in as clear a way as possible. This will consist of two steps: 1)
we need to review the literature and understand what its achievements are; 2)
we need to implement a GP system and show how our system differs from a GP
system in practice.

An implementation of a symbolic regression genetic programming system is
TinyGP, Java source code for which can be found in Appendix B
of~\cite{poli08:fieldguide}.

There are five basic things that need to be specified in order to create a GP
algorithm. We need to determine the terminal set, the function set, the fitness
function, the GP parameter values, and the terminal solution designation. The
terminal set consists of the external inputs (i.e.  variables of the form x, y,
etc.), functions with no arguments (e.g., rand and other functions with side
effects), and constants.

The function set is a set of functions and their arities. Function sets must
satisfy \emph{closure}, which consists of \emph{type consistency} and
\emph{evaluation safety}. Type consistency means that all functions return
values of the same type. Evaluation safety means that functions do not throw
errors.

The fitness function is the objective function.

The GP parameters are various: population size, probabilities of performing
genetic operations (crossover and mutation), selection mechanism, etc.

Finally, we need to specify termination condition. These include the number of
runs or other predicates based on which the program should terminate.

There are several papers by O'Reilly that analyze GP that are worth looking at:
\cite{OReilly:thesis} \cite{OReilly:1995:tabbGP}

\subsection{Modulearity and Hierarchy in GP}

Koza's Automatically defined functions (ADFs) are the most popular way of
evolving reusable components. In automatically defined functions, we explicitly add auxiliary functional genetic material that the main function can call. Typically, the ADFS need different terminal and function sets (for example, ADFs need argument terminals). In this scheme, each function only has access to its own ADFs. See Olsson's ADATE system where subfunctions as anonymous lambda expressions are extracted~\cite{DBLP:conf/eurogp/Olsson9}.
